---
title: "{{ cookiecutter.project_name }} - Example Report"
author: "{{ cookiecutter.author_name }}"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
    code_folding: hide
  pdf_document:
    toc: true
    number_sections: true
params:
  data_file: "example_data.csv"
---

```{r setup, include=FALSE}
# Setup chunk
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 8,
  fig.height = 6,
  fig.align = "center",
  cache = FALSE
)

# Load required libraries
library(here)
{% if cookiecutter.include_tidyverse == 'y' %}
library(tidyverse)
library(DT)
{% endif %}
{% if cookiecutter.include_plotly == 'y' %}
library(plotly)
{% endif %}
```

# Introduction

This is an example R Markdown report for **{{ cookiecutter.project_name }}**.

## Project Overview

- **Project**: {{ cookiecutter.project_name }}
- **Description**: {{ cookiecutter.project_description }}
- **Author**: {{ cookiecutter.author_name }}
- **R Version**: {{ cookiecutter.r_version }}
- **Report Generated**: `r Sys.Date()`

# Data Loading and Preprocessing

```{r data-loading}
# Example data loading (uncomment when you have data)
# data_path <- here("data", "raw", params$data_file)
# if (file.exists(data_path)) {
#   raw_data <- read.csv(data_path)
# } else {
#   # Create example data for demonstration
#   raw_data <- data.frame(
#     id = 1:100,
#     value = rnorm(100, 50, 10),
#     category = sample(c("A", "B", "C"), 100, replace = TRUE),
#     date = seq(Sys.Date() - 99, Sys.Date(), by = "day")
#   )
# }

# For demo purposes, create example data
raw_data <- data.frame(
  id = 1:100,
  value = rnorm(100, 50, 10),
  category = sample(c("A", "B", "C"), 100, replace = TRUE),
  date = seq(Sys.Date() - 99, Sys.Date(), by = "day")
)
```

{% if cookiecutter.include_tidyverse == 'y' %}
```{r data-processing}
# Data processing with tidyverse
processed_data <- raw_data %>%
  janitor::clean_names() %>%
  dplyr::mutate(
    value_scaled = scale(value)[, 1],
    week = lubridate::week(date)
  ) %>%
  dplyr::filter(!is.na(value))

# Summary statistics
summary_stats <- processed_data %>%
  dplyr::group_by(category) %>%
  dplyr::summarise(
    count = n(),
    mean_value = mean(value, na.rm = TRUE),
    sd_value = sd(value, na.rm = TRUE),
    min_value = min(value, na.rm = TRUE),
    max_value = max(value, na.rm = TRUE),
    .groups = "drop"
  )
```
{% endif %}

# Exploratory Data Analysis

## Summary Statistics

```{r summary-table}
{% if cookiecutter.include_tidyverse == 'y' %}
# Interactive table with DT
DT::datatable(
  summary_stats,
  options = list(
    pageLength = 10,
    scrollX = TRUE
  ),
  caption = "Summary Statistics by Category"
) %>%
  DT::formatRound(columns = c("mean_value", "sd_value"), digits = 2)
{% else %}
# Basic summary
summary(raw_data)
{% endif %}
```

## Data Visualization

```{r plots, fig.cap="Distribution of Values by Category"}
{% if cookiecutter.include_tidyverse == 'y' %}
# Create visualizations with ggplot2
p1 <- ggplot(processed_data, aes(x = category, y = value, fill = category)) +
  geom_boxplot(alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.3) +
  labs(
    title = "Distribution of Values by Category",
    x = "Category",
    y = "Value",
    fill = "Category"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

{% if cookiecutter.include_plotly == 'y' %}
# Make interactive with plotly
ggplotly(p1, tooltip = c("x", "y"))
{% else %}
print(p1)
{% endif %}
{% else %}
# Basic R plotting
boxplot(value ~ category, data = raw_data, 
        main = "Distribution of Values by Category",
        xlab = "Category", ylab = "Value")
{% endif %}
```

```{r time-series, fig.cap="Time Series of Values"}
{% if cookiecutter.include_tidyverse == 'y' %}
# Time series plot
p2 <- ggplot(processed_data, aes(x = date, y = value, color = category)) +
  geom_line(alpha = 0.7) +
  geom_smooth(method = "loess", se = FALSE) +
  labs(
    title = "Time Series of Values",
    x = "Date",
    y = "Value",
    color = "Category"
  ) +
  theme_minimal()

{% if cookiecutter.include_plotly == 'y' %}
ggplotly(p2)
{% else %}
print(p2)
{% endif %}
{% else %}
# Basic time series plot
plot(raw_data$date, raw_data$value, type = "l",
     main = "Time Series of Values",
     xlab = "Date", ylab = "Value")
{% endif %}
```

# Analysis Results

## Key Findings

1. **Data Overview**: The dataset contains `r nrow(raw_data)` observations across `r ncol(raw_data)` variables.

{% if cookiecutter.include_tidyverse == 'y' %}
2. **Category Distribution**: 
   - Category A: `r summary_stats$count[summary_stats$category == "A"]` observations
   - Category B: `r summary_stats$count[summary_stats$category == "B"]` observations  
   - Category C: `r summary_stats$count[summary_stats$category == "C"]` observations

3. **Value Statistics**:
   - Overall mean: `r round(mean(processed_data$value), 2)`
   - Overall standard deviation: `r round(sd(processed_data$value), 2)`
   - Range: `r round(min(processed_data$value), 2)` to `r round(max(processed_data$value), 2)`
{% endif %}

## Statistical Tests

```{r statistical-tests}
{% if cookiecutter.include_tidyverse == 'y' %}
# ANOVA test
anova_result <- aov(value ~ category, data = processed_data)
anova_summary <- summary(anova_result)

# Extract p-value
p_value <- anova_summary[[1]][["Pr(>F)"]][1]

cat("ANOVA Results:\n")
cat("F-statistic:", round(anova_summary[[1]][["F value"]][1], 4), "\n")
cat("p-value:", round(p_value, 4), "\n")
cat("Significant difference between categories:", ifelse(p_value < 0.05, "Yes", "No"), "\n")
{% else %}
# Simple t-test example
t_test_result <- t.test(raw_data$value)
cat("One-sample t-test results:\n")
cat("t-statistic:", round(t_test_result$statistic, 4), "\n")
cat("p-value:", round(t_test_result$p.value, 4), "\n")
{% endif %}
```

# Conclusions

This example report demonstrates:

1. **Data Loading**: How to load and validate data files
2. **Data Processing**: Basic data cleaning and transformation
3. **Visualization**: Creating informative plots and charts
4. **Analysis**: Performing statistical tests and interpreting results
5. **Documentation**: Generating reproducible reports

## Next Steps

- [ ] Add more sophisticated analysis methods
- [ ] Include additional visualizations
- [ ] Implement model validation
- [ ] Add cross-validation procedures
- [ ] Create interactive dashboards

# Session Information

```{r session-info}
# Display session information for reproducibility
sessionInfo()
```

---

*Report generated on `r Sys.Date()` using {{ cookiecutter.project_name }} template.* 